%  Special terms

\newglossaryentry{docker}{
    name=Docker,
    description={Docker is a set of platform as a service products that use OS-level virtualization to deliver software in packages called containers.}
}

\newglossaryentry{gazebo}{
    name=Gazebo,
    description={Gazebo is an open-source 3D robotics simulator.}
}

\newglossaryentry{linux}{
    name=Linux,
    description={GNU/Linux is a family of open-source Unix-like operating systems based on the Linux kernel, an operating system kernel first released on September 17, 1991, by Linus Torvalds.}
}

\newglossaryentry{wifi}{
    name=Wi-Fi,
    description={Wi-Fi is a family of wireless network protocols based on the IEEE 802.11 family of standards.}
}

\newglossaryentry{pytorch}{
    name=PyTorch,
    description={PyTorch is a machine learning framework based on the Torch library, used for applications such as computer vision and natural language processing.}
}

\newglossaryentry{psutil}{
    name=psutil,
    description={Process and system utilities (psutil) is a cross-platform library for retrieving information on running processes and system utilization (CPU, memory, disks, network, sensors) in Python.}
}

\newglossaryentry{cadvisor}{
    name=cAdvisor,
    description={cAdvisor (Container Advisor) provides container users an understanding of the resource usage and performance characteristics of their running containers.}
}

\newglossaryentry{python}{
    name=Python,
    description={Python is a high-level, general-purpose programming language.}
}

\newglossaryentry{fast_dds}{
    name=Fast-DDS,
    description={eprosima Fast DDS (formerly Fast RTPS) is a C++ implementation of the DDS (Data Distribution Service) standard of the OMG (Object Management Group).}
}

\newglossaryentry{openvino}{
    name=OpenVINO,
    description={OpenVINO is an open-source toolkit for optimizing and deploying deep learning models on Intel hardware. It provides boosted deep learning performance for vision, audio, and language models from popular frameworks like TensorFlow, PyTorch, and more.}
}

\newglossaryentry{yolo}{
    name=YOLO,
    description={YOLO, an acronym for You Only Look Once, is a one-stage object detection algorithm.}
}

% Acronyms
\newacronym{rtt}{RTT}{Round-Trip Time}

\newacronym{iot}{IoT}{Internet of Things}

\newacronym{md}{MD}{Mobile Devices}

\newacronym{tsn}{TSN}{Time-Sensitive Network}

\newacronym{netem}{NetEm}{Network Emulator}

\newacronym{ifb}{IFB}{Intermediate Functional Block}

\newacronym{amr}{AMR}{Autonomous Mobile Robot}

\newacronym{ai}{AI}{Artificial Intelligence}

\newacronym{mec}{MEC}{Multi-Access Edge Computing}

\newacronym{slam}{SLAM}{Simultaneous Localization and Mapping}  

\newacronym{mcc}{MCC}{Multi-Access Cloud Computing}

\newacronym{hrc}{HRC}{Human-Robot Collaboration}

\newacronym{ros}{ROS}{Robot Operating System}

\newacronym{nuc}{NUC}{Intel Next Unit of Computing}

\newacronym{sma}{SMA}{Simple Moving Average}

\newacronym{dds}{DDS}{Data Distribution System}

\newacronym{qos}{QoS}{Quality of Service}

\newacronym{gpu}{GPU}{Graphics Processing Unit}

\newacronym{cpu}{CPU}{Central Processing Unit}

\newacronym{dnn}{DNN}{Deep Neural Network}

\newacronym{cnn}{CNN}{Convolutional Neural Network}

\newacronym{ap}{AP}{Average Precision}

\newacronym{map}{mAP}{Mean Average Precision}

\newacronym{coco}{COCO}{Common Object in Context}

\newacronym{rapl}{RAPL}{Running Average Power Limit}

\newacronym{fov}{FOV}{Field of View}

\newacronym{udp}{UDP}{User Datagram Protocol}

\newacronym{tcp}{TCP}{Transmission Control Protocol}

\newacronym{rtps}{RTPS}{Real-time Publish-Subscribe}

\newacronym{fps}{FPS}{frames per second}

\newacronym{dl}{DL}{Deep Learning}

\newacronym{rl}{RL}{Reinforcement Learning}

\newacronym{drl}{Deep RL}{Deep Reinforcement Learning}

\newacronym{rgb}{RGB}{Red-Green-Blue}

\newacronym{nms}{NMS}{Non-maximum Suppression}

\newacronym{io}{IO}{Input/Output}

\newacronym{sdf}{SDFormat}{Simulation Description Format}

\newacronym{vm}{VM}{Virtual Machine}

\newacronym{wan}{WAN}{Wide Area Network}

\newacronym{ran}{RAN}{Radio Access Network}

\newacronym{kpi}{KPI}{Key Performance Indicator}

\newacronym{rpn}{RPN}{Region Proposal Network}

\newacronym{roi}{RoI}{Region of Interest}

\newacronym{ne}{NE}{Nash Equilibrium}

\newacronym{dqn}{DQN}{Deep Q-learning Network}

\newacronym{a2c}{A2C}{Advantage Actor Critic}

% Acronyms for schools and labs
\newacronym{amsrl}{AMSRL}{Autonomous Mobile System Research Lab}

\newacronym{tum}{TUM}{Technical University of Munich}
