% In total max. 1 Page!
\RAIstudentthesisAbstract{%
%
% Abstract English:
To achieve autonomy, \acp{amr} need to run different computation and memory intensive algorithms, such as perception, \ac{slam}, path planning, and learning. However, an \ac{amr}'s on-board computational and energy resources are limited by space restrictions and battery lifetime. With the emergence of edge computing, \acp{amr} have the opportunity to offload costly computation tasks to the edge, while only a small portion of the computation remains on the on-board system. However, depending on the application scenarios, offloading certain tasks from the \ac{amr} to the edge at all times may not be possible, beneficial or even feasible due to the network's latency, dynamic network changes, and resource availability. On the other hand, offloading computational workloads to the edge could impact the robot's safety, availability as well as on-board resources. The exact influence on the robotic system will depend on the chosen offloading strategy. Therefore, this thesis uses 2D object detection as an offloading task and investigates the performance and the latency, as well as the CPU usage and power consumption of the robot's on-board system under diffferent offloading strategies. 
% Furthermore, this thesis implements a decision-making offloading strategy based on the network conditions and robot's on-board system states to minimize the latency, but is also subjected to restrictions of the power consumption and CPU usage.
}{%
%
% Zusammenfassung Deutsch:
Die autonomen mobilen Roboter müssen verschiedene rechnen- und speicherintensive Algorithmen ausführen. 
}%
%
%
